Global Assessments of Fishery Status need Better Data more than Better Models

### 2020-08-28 documents/ovando-etal-assessing-global-fisheries.Rmd
methods almost fixed

---
title: "Global Assessments of Fishery Status need Better Data more than Better Models"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yannick Rousseau
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::pdf_document2: default
params:
  results_name: ["v0.5"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, formulating evidence-based policy and tracking the implementation of the United Nations Sustainable Development Goals. While we have reliable estimates of stock status for fisheries accounting for 50% of global catch, our knowledge of the state of the remaining 50%, the worlds 'unassessed' fisheries, is poor. Numerous high-profile publications featuring a range of statistical methods have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methdological differences have produced counterintuitive and conflicting results. This is especially true in areas such as Southeast Asia and Africa which are also regions that have high dependence on fishery resources. How can we effectively estimate the state of global fishery sustainability and track progress towards the Sustainable Development Goals targets? We developed a flexible assessment model to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion through Fisheries Management Index scores, and increasingly available but historically underutilized data such as trawl footprints and effort data. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world, and to identify priority data types for future collection. Our results provide further evidence that catch data by themselves cannot provide reliable estimates of fishery health. Our ability to obtain reliable estimates of stock status for the world's unassessed fisheries depends on prioritizing the collection of key data at a global scale, not on the development of new modeling methods alone.
always_allow_html: true
---

@@

## Model Overview

The core of `sraplus` is a Pella-Tomlinson [@pella1969] production model  in the manner of @winker2018. While models of these kinds abstract away many important details of fish biology and fleet behavior, they are the highest resolution model that the potential data evaluated here will support. The purpose of `sraplus` is not to make substantial improvements in the fitting of surplus production models, but to provide a flexible tool for exploring the impacts of adding different kinds of data and priors on estimates of fishery status. Detailed examples of how to operate the code of the model can be found [github.com/danovando/sraplus](https://github.com/DanOvando/sraplus). Here we describe the overall methods used to produce the results in this paper and highlight key details.

@@

Suppose that the only thing we observe from a fishery is a catch history. Assuming Pella-Tomlinson population dynamics, the only thing we can learn from this catch history alone is the set of model parameters that ensure that the population still exists and never collapsed in the past (i.e. that catches have never been greater than biomass). We can think of this as a binomial process in which we fit a model of the population, conditional on catches, to the fact that we know that population existed in each time step of the catch history.  Beyond that though, baring additional information we have no way of knowing whether these catches represent a substantial proportion of a small population or a minuscule fraction of a massive population; all we know is that the current population must be greater than 0 and less than or equal to carrying capacity *k*.

@@

For our case study fishery, we can use `sraplus` as a filter to say, conditional on our priors, the catch history, and the population model, what is our implied prior on stock status of the fishery over time (see Section XX and Table.\@ref(tab:prior-tab) for descriptions of model parameters). While user defined priors on population parameters can be supplied, `sraplus` has a number of built in mechanisms for setting parameters based on the taxonomy of the species in question and the magnitude of the catch history. This form of analysis is often extended though to include an explicit prior on stock status in the most recent year [@walters2006].

@@

ex %>% 
  ggplot(aes(year, b_v_bmsy)) + 
  geom_point()

co_driors <- sraplus::format_driors(taxa = unique(ex$scientificname),
                                 catch = ex$catch, 
                                 years = ex$year,
                                 terminal_state = 0.25,
                                 terminal_state_cv = 0.25,
                                 b_ref_type = "k")

plot_driors(co_driors)

plot_sraplus(`biased fit` = biased_co_fit, `unbiased fit` = co_fit)

@@

pull out example from SAR fits
```{r}
sar <- sraplus::sar %>% 
  filter(stockid %in% unique(ram_data$stockid)) %>% 
  arrange(desc(sar)) %>% 
  select(stockid, everything()) %>% 
  slice(10)

ex <- ram_data %>% 
  filter(stockid %in% unique(sar$stockid))

ex %>% 
  ggplot(aes(year, b_v_bmsy)) + 
  geom_point()

co_driors <- sraplus::format_driors(taxa = unique(ex$scientificname),
                                 catch = ex$catch, 
                                 years = ex$year,
                                 terminal_state = 0.25,
                                 terminal_state_cv = 0.25,
                                 b_ref_type = "k")

plot_driors(co_driors)

plot_sraplus(`biased fit` = biased_co_fit, `unbiased fit` = co_fit)

# fit using SAR

sar_driors <- sraplus::format_driors(taxa = unique(ex$scientificname),
                                 catch = ex$catch, 
                                 years = ex$year,
                                 sar = sar$sar[sar$stockid == unique(ex$stockid)])

plot_driors(sar_driors)

sar_fit <- fit_sraplus(sar_driors, estimate_shape = TRUE)

plot_sraplus(`biased fit` = biased_co_fit, `unbiased fit` = co_fit, `sar fit` = sar_fit)

# fit using biomass index

index_driors <- sar_driors <- sraplus::format_driors(taxa = unique(ex$scientificname),
                                 catch = ex$catch, 
                                 years = ex$year,
                                 sar = sar$sar[sar$stockid == unique(ex$stockid)],
                                 index = ex$b_v_bmsy[!is.na(ex$b_v_bmsy)], 
                                 index_years = ex$year[!is.na(ex$b_v_bmsy)])

index_fit <- fit_sraplus(index_driors, engine = "stan", estimate_shape = TRUE)

plot_sraplus(`biased fit` = biased_co_fit, `unbiased fit` = co_fit, `sar fit` = sar_fit,
             `index fit` = index_fit,
             plotvars = "b_div_bmsy") + 
  geom_point(data = ex, aes(year, b_v_bmsy))

@@

```{r prior-tab}
cd <- data_frame(Parameter = "Carrying Capacity", Abbreviation = "K", `Default Prior` = "$logn(10\\times{max(catch)},4)$") %>%
  rbind(c("Growth rate", "r", "$logn(r_{fishlife}, \\sigma_{r,fishlife})$")) %>%
  rbind(c("Shape parameter", "m", "$logn(1.01, 0.25)$")) %>%
  rbind(c("Catchability", "q", "$logn(1e^{-3}, 0.3)$")) %>%
  rbind(c("Observation Error", "$\\sigma_{obs}$", "$logn(.05,2)$")) %>%
  rbind(c("Process Error", "$\\sigma_{proc}$", "$logn(.05,0.5)$")) %>% 
  rbind(c("Tech Creep", "$creep$", "$logn(0.025,0.2)$"))

@@

@@

## FMI and SAR Based Priors

All prior regression models where tested by out-of-sample predictive power, and where competing models were considered the final model was chosen by leave-on-out validation [xx citation]. These models are intended as a reasonably robust means of translating available data into usable prior for our model. Given the scope of this analysis, we do not claim that the presented regressions are the best possible model relating these data with fishery status indicators of interest. Rather, each regression was tested to ensure that it is unlike that, given the same data, and alternative model would be unlikely to perform much better than those presented here XX this might be too much defenseXX

For each statistical prior, we fit three different models, relating the data of interesting, e.g. swept area ratio (SAR), to each of *B/B~MSY~*, *F/F~MSY~*, and *F*

### Swept Area Ratio Priors

## Fisheries Management Index Priors

## Catch-Only Priors

## Effort Data

While the FMI and SAR data show some potential for estimating U/U~MSY~ and B/B~MSY~ values, they are clearly not an ideal measure of stock status. An alternative is to actually develop indices of abundance that we can fit models to. @rousseau2019 provides a useful starting place for this exercise, presenting estimates of fishing effort throughout the globe from 1950 to 2015.  Merging these data with capture statistics can provide a crude CPUE index that can then be used to fit a surplus production model. Developing an index of abundance in this manner is clearly a very rough analysis only intended to illustrate broad concepts. Any analysis of CPUE data can be severely affected by changes in technology, skill, hyperdepletion, hyperstability, changes in the spatial footprint of the fishery, and selectivity [@maunder2004a; @walters2003]. In the case of this analysis, a kilowatt day of fishing with 1950s technology clearly represents a different amount of fishing power than a kilowatt day of fishing in 2012. To account for this somewhat, @rousseau2019 include a 2.6% annual "technological creep" factor, which we incorporate in our analysis.

@rousseau2019 measure an index of abundance as catch divided by their effort index, either nominal or effective (assuming the 2.6\% technology rate). This assumes that every unit increase in effort is linearly greater than the unit of effort before it. When effort increases dramatically above historic levels, this can create a CPUE index that decreases faster than the true population. This is due to the fact that the marginal fishing mortality produced by increasing unit of efforts increases decreases as effort approaches infinity (since fishing mortality is bounded between 0 and 1). To accommodate this, we generate a catch per effective harvest rate index of abundance, as

$$I_t = \frac{catch_t}{(1 - e^{-q_tE_t})}$$

>>>>

---
title: "Global Assessments of Fishery Status need Better Data more than Better Models"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yannick Rousseau
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::pdf_document2: default
  bookdown::word_document2:
    reference_docx: word-template.docx
params:
  results_name: ["v0.5"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, formulating evidence-based policy and tracking the implementation of the United Nations Sustainable Development Goals. While we have reliable estimates of stock status for fisheries accounting for 50% of global catch, our knowledge of the state of the remaining 50%, the worlds 'unassessed' fisheries, is poor. Numerous high-profile publications featuring a range of statistical methods have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methdological differences have produced counterintuitive and conflicting results. This is especially true in areas such as Southeast Asia and Africa which are also regions that have high dependence on fishery resources. How can we effectively estimate the state of global fishery sustainability and track progress towards the Sustainable Development Goals targets? We developed a flexible assessment model to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion through Fisheries Management Index scores, and increasingly available but historically underutilized data such as trawl footprints and effort data. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world, and to identify priority data types for future collection. Our results provide further evidence that catch data by themselves cannot provide reliable estimates of fishery health. Our ability to obtain reliable estimates of stock status for the world's unassessed fisheries depends on prioritizing the collection of key data at a global scale, not on the development of new modeling methods alone.
always_allow_html: true
---

@@

`sraplus` contains too many options to cover within this methods section. We encourage readers to explore the documentation available at the package website at www.github.com/danovando/sraplus. Below we describe the structure of the population model underpinning `sraplus`, the estimation model, and a brief example demonstrating the use of the model.

The core of `sraplus` is a Pella-Tomlinson [@pella1969] production model constructed in the manner of @winker2018. While models of these kinds abstract away many important details of fish biology and fleet behavior, they are the highest resolution model that the potential data evaluated here will support. The purpose of `sraplus` is not to make substantial improvements in the fitting of surplus production models, but to provide a flexible tool for exploring the impacts of adding different kinds of data and priors on estimates of fishery status

Where $B_t$ is biomass at time *t*, *r* is the intrinsic growth rate, *m* is the scaling parameter that allows for the ratio of B~msy~/K to shift. When *m* is two Bmsy / K = 0.5 and the model acts as a Schaefer model, lower values of m shift the production function left, higher values right. *c* is catch, and *p* is process error. Growth rates can become unrealistically large when the population reaches low sizes under the Pella-Tomlinson model. We deal with this problem by following the methods described in @winker2018. to reduce the production of the population when it falls below a threshold of 25% of carrying capacity.

We  allow for process error *p* (in the manner of the stochastic stock reduction analysis error suggested by @walters2006). This allows the population dynamics to deviate from the exact values given by the Pella-Tomlinson operating model, while still conforming to the assumptions of this model on average. Incorporation of process errors is useful for two reasons: (1) when you have an abundance index, process errors can reduce bias arising from lack of fit in a deterministic SRA whenever dynamics are poorly explained by catch-history alone, and (2) with or without an abundance index (or other info), the stochastic portion is necessary to get good uncertainty intervals (i.e., with close to nominal coverage, see @thorson2018).

Process error *p* is assumed to be log-normally distributed, such that

## Estimation Model

All of our estimates are Bayesian in nature. We can break the use of `sraplus` into two distinct categories: with data and without. By "data", we refer to measurements which are used to confront model estimates within a likelihood function. In our context, these include fishery-independent survey data, or a CPUE index. When there are no data, the model amounts to filtering priors through the model (the combination of the Pella-Tomlinson operating model and the catches for the stock in question, along with any fixed parameters). Under this mode, the model is essentially a stock-reduction analysis model, in the manner of @walters2006, in which we ask, which combinations of prior probability distributions of parameters do not crash the population (i.e. results in biomass less than catches in any time step in the fishery's history), given the constraints of the population model.

The full list of estimable parameters are listed in Table.\@ref(tab:param-tab). *r* and *k* are the only two parameters that are always estimated. Estimation of every other parameter can be turned on or off. When estimation is turned off estimable parameters are fixed at their initial values, which can either be set to model defaults or specified by the user. For our main sets of results (everything excluding the value of information analysis), the estimated parameters are *r*, *k*, *m*, $\sigma_{obs}$, $\gamma$, and *B0*. *q* is also estimated when needed.

```{r param-tab}
cd <- data_frame(Parameter = "Carrying Capacity", Abbreviation = "K", `Default Prior` = "$logn(10\\times{max(catch)},4)$") %>%
  rbind(c("Growth rate", "r", "$logn(r_{fishlife}, \\sigma_{r,fishlife})$")) %>%
  rbind(c("Shape parameter", "m", "Drawn from @horson2012")) %>%
  rbind(c("Catchability", "q", "$logn(1e^{-3}, 0.3)$")) %>%
  rbind(c("Observation Error", "$\\sigma_{obs}$", "$logn(.05,2)$")) %>%
  rbind(c("Ratio of process to observation error", "$\\gamma$", "$logn(.05,0.5)$")) %>%
  rbind(c("Tech Creep", "$creep$", "$logn(0.025,0.2)$")) %>% 
  rbind(c("Initial State", "$B0$", "$logn(0.025,0.2)$"))

knitr::kable(
  cd,
  "latex",
  align = "l",
  escape = F,
  row.names = F,
  caption = "Potential parameters included in sraplus, abbreviations, and default priors"
) %>%
  kableExtra::kable_styling(full_width = T, font_size = 9) %>%
  kableExtra::row_spec(0, bold = T)
```

`sraplus` can be run in two forms: either as a stock reduction analysis [SRA,@walters2006], or fit to an index of abundance (fishery dependent or independent). Unless there is an abundance index to fit to the model runs as a stock reduction analysis. A stock reduction analysis works by specifying prior distributions on population parameters and critically the recent state of the fishery. `sraplus` allows users to specify the most recent status in units of depletion, B/B~MSY~, F, or F/F~MSY~. We then sample from the prior distributions of the population model parameters and apply those to the production model, along with the catch history. Any run that results in the collapse of the population (catch greater than biomass in any time step) is immediately rejected. The remaining viable draws from the prior distributions are sampled in proportion to the supplied prior on recent stock status. It is critical to note that a stock reduction analysis is only a mechanism for revealing implicit priors on fishery status and parameters through a sample-importance-resampling algorithm: the model cannot learn anything new about stock status in the absence of additional data to fit to, beyond the prior on stock status that is fed to it. The usefullness of this process then is in filling in the gap of parameters of interest (e.g. maximum sustainable yield, MSY), and providing historic values of stock status. Any model results based on data sources listed in Table.\@ref(tab:dat-description) that do not contain "cpue" or "RAM data" is estimated through stock reduction analysis.

When an index of abundance is available the model estimates the posterior probability distributions of the estimated and transformed parameters using Hamiltonian Monte Carlo implemented in stan [@standevelopmentteam2018] accessed through the `tmbstan` interface [@monnahan2018]. The model fits to a direct estimate of abundance (e.g. a fishery independent survey or a standardized catch-per-unit-effort index), the likelihood is

$$log(\pmb{A_t}) \sim normal(f(r,k,m,B0,\pmb{p},\pmb{C}) \times q, sigma_{obs{}}) $$
where *f* is the Pella-Tomlinson produciton model (Equation 1.XX). When an effort index is available, `sraplus` constructs an index of abundance based on the catch and effort data. @rousseau2019 measure an index of abundance as catch divided by their effort index, either nominal or effective (assuming the 2.6\% technology rate). This assumes that every unit increase in effort is linearly greater than the unit of effort before it. When effort increases dramatically above historic levels, this can create a CPUE index that decreases faster than the true population. This is due to the fact that the marginal fishing mortality produced by increasing unit of efforts increases decreases as effort approaches infinity (since fishing mortality is bounded between 0 and 1). To accommodate this, we generate a catch per effective harvest rate index of abundance, as

$$cpue_t = \frac{catch_t}{(1 - e^{-q_tE_t})}$$

We then fit to the index of abundance per

$$log(cpue_t) \sim normal(f(r,k,m,B0,\pmb{p},\pmb{C}), sigma_{obs{}})$$

## Priors

Priors for all estimable parameters can be left at default values or set by the user. The shape parameter is usually not reliably estimable given available data for surplus production models, however, @thorson2012 provides estimate the ratio of B~MSY~ to K for many fish taxa. While we estimate *m* by default throughout the results presented here, we use highly informative priors for the shape parameter drawn from @thorson2012 based on the genus of the species in question.

We address two critical features of prior use in sraplus below: tuning of the prior-predictive distribution and translation of outside data into priors usable by sraplus.

### Prior Predictive Tuning

Suppose that the only thing we observe from a fishery is a catch history. Assuming Pella-Tomlinson population dynamics, the only thing we can learn from this catch history alone is the set of model parameters that ensure that the population still exists and never collapsed in the past. We can think of this as a binomial process in which we fit a model of the population, conditional on catches, to the fact that we know that population existed in each time step of the catch history.  Beyond that though, baring additional information we have no way of knowing whether these catches represent a substantial proportion of a small population or a minuscule fraction of a massive population; all we know is that the current population must be greater than 0 and less than or equal to carrying capacity *k*.

In the absence of any data to fit to, the SRA algorithm works by assuming that we know current stock status, and then finds feasible parameters to satisfy that belief. This creates a problem for the Bayesian nature of our analysis though. Consider a production model with two parameters, a growth rate *r* and a carrying capacity *k*. Once we specify prior distributions on r and k, and then apply these distributions to our model (the shape of the production function along with the catch histories), we have implicitly provided a prior on the status of the stock in all time periods, since each unique combination of r and k together with the model produces a deterministic stock status in each time step. Doing so places essentially two priors on recent stock status: one implicit prior through the population parameter priors, and one explicit through the users perception of recent stock status, creating a problem termed Borel's Paradox. This may seem like an academic concern, and indeed in our experience when the data are sufficiently informative the Bayesian version of our model subject to Borel's paradox produces effectively identical results to those produce by the same model fit by maximum likelihood. However, particularly for the SRA version of `sraplus`, Borel's Paradox poses a particular problem.

The SRA algorithm works in two steps. First, the algorithm rejects any draws that resulted in the collapse of the population (biomass less than catch in a given timestep). From there a standard SRA would sample from the priors in proportion to the stated prior on recent stock status. If the bulk of the prior on terminal stock status was concentrated at 50% of *k*, combinations of *r* and *k* that produce terminal stock status near 50% of *k* are sampled proportionally more frequently. However, lower values of terminal stock status have fewer candidate values of *r* and *k*, since it becomes harder and harder to find viable pairs that come close to but do not crash the population at any time step. Conversely, in the absence of constraints higher values of stock status have infinite combinations of plausible *r* and *k* combinations: since under this model the population cannot be greater than carrying capacity, as for example *k* approaches infinity terminal stock status asymptotes at close to 100% of *k*. The net result of this is that even though individual combinations of *r* and *k* that produce higher stock status than the mean of the prior on recent stock status individually have lower probability of being sampled, there are many more opportunities for the lower-probability events that produce higher stock status to be sampled. As a result, the post-model-pre-data prior on terminal depletion will always be higher under this method than the supplied prior on stock status.

And we then perform a second SIR algorithm but now sampling each observation $n_i$ in proportion to $p(n_i)$. The net result of this is a post-model-pre-data distribution of parameters *r* and *k*  that produce a distribution of recent stock status that roughly matches the supplied prior on recent stock status. In effect, this process answers the question "given the model, what combinations of parameters produce my prior on recent stock status". This is only an approximate solution, but it helps ensure that the post-model-pre-data distribution of stock status much more closely matches the stated prior on recent stock status, and reduced the positive bias resulting from use of the raw SRA algorithm (Fig.\@ref(fig:bias-plot)).

```{r bias-plot, fig.cap = "Post-model-pre-data distribution of depletion (biomass relative to carrying capacity) from raw SRA algorithm (untuned, top row), from SRA algorithm with approximate tuning applied (tuned, middle row), compared to the supplised prior on depletion (bottom row). Black vertical line indicates median value. "}

co_driors <- sraplus::format_driors(taxa = unique(ex$scientificname),
                                 catch = ex$catch, 
                                 years = ex$year,
                                 terminal_state = 0.25,
                                 terminal_state_cv = 0.5,
                                 b_ref_type = "k")

biased_depletion <- biased_co_fit$fit %>% 
  filter(variable == "dep_t") %>%
  filter(year == max(year)) %>% 
  mutate(set = "Untuned Post-Model-Pre-Data") %>% 
  select(year, value, set)

tuned_depletion <- co_fit$fit %>% 
  filter(year == max(year), variable == "dep_t") %>% 
  mutate(set = "Tuned Post-Model-Pre-Data") %>% 
  select(year, value, set)

prior <- tuned_depletion %>% 
  mutate(value = rlnorm(n(), log(0.25), 0.5)) %>% 
    mutate(set = "Prior")

comps <- biased_depletion %>% 
  bind_rows(tuned_depletion) %>% 
  bind_rows(prior) %>% 
  group_by(set) %>% 
  mutate(valrank = percent_rank(value)) %>% 
  filter(between(valrank, .05, .95))

comps %>% 
  ggplot(aes(x = value, y = set)) + 
  ggridges::geom_density_ridges(alpha = 0.9,
                                quantile_lines = TRUE, quantiles = 2) +
  scale_x_continuous(limits = c(0, 1.2), name = "Depletion (B/K)") + 
  scale_y_discrete(name = '')

### Priors Informed by Outside Data

Along with allowing users to supply their own priors, the `sraplus` package contains three classes of built in methods for converting information on stock status from additional outside data into a form usable as a prior by `sraplus`. We paired data on catch histories, swept area ratio (SAR), and fisheries management index (FMI) with estimates of stock status from the RAM legacy stock assessment database. We then train a model of the general form $log(status) \sim normal(variable,\sigma)$ for each of these three data types. Given values of these variables for a new fishery then, `sraplus` uses the fitted model to generate posterior predictive distributions of stock status based on these data, which can then be used as priors on stock status by `sraplus`.

All prior regression models where tested by out-of-sample predictive power, and where competing models were considered the final model was chosen by leave-on-out validation [xx citation]. These models are intended as a reasonably robust means of translating available data into usable prior for our model. Given the scope of this analysis, we do not claim that the presented regressions are the best possible model relating these data with fishery status indicators of interest. Rather, each regression was tested to ensure that it is unlikely that, given the same data, and alternative model would be unlikely to perform much better than those presented here.

#### Catch-Only Priors

#### Fisheries Management Index Priors

#### Swept Area Ratio Priors

## Example Use of `sraplus`

@@

@@

For our case study fishery, we can use `sraplus` as a filter to say, conditional on our priors, the catch history, and the population model, what is our implied prior on stock status of the fishery over time (see Section XX and for descriptions of model parameters). While user defined priors on population parameters can be supplied, `sraplus` has a number of built in mechanisms for setting parameters based on the taxonomy of the species in question and the magnitude of the catch history. This form of analysis is often extended though to include an explicit prior on stock status in the most recent year [@walters2006].

@@

@@

@@

@@

\begin{equation}
  f(x)=\begin{cases}
      B_{t + 1} = \left(B_{t} + B_{t}\frac{r}{m - 1}\left(1 - \left(\frac{B_t}{K}\right)^{m- 1}\right) - \hat{c_t}\right)p_t
, & \text{if $B_t>0.25 \times K$}.\\
     B_{t + 1} = \left(B_{t} + \frac{B_{t}}{0.25 \times K}\left(B_{t}\frac{r}{m - 1}\left(1 - \left(\frac{B_t}{K}\right)^{m- 1}\right) - \hat{c_t}\right)\right)p_t, & \text{otherwise}.
  \end{cases}
  (\#eq:sihockey)
\end{equation}

@@

\begin{equation}
  p_t \sim e^{normal\left(-\sigma_{proc}^2/2,\sigma_{proc}\right)}
  (\#eq:siprocerror)
\end{equation}
